\chapter{Related Work}
ABE schemes have seend rapidly developed over the recent years and so enjoyed a wide field of related work. Since ABE offeres a great feature wirarity (fine-graint access control \cite{goyal2006attribute}, contant sized cipher-text \cite{li2017two}, efficient en-, re- and decryption \cite{yang2013dac} etc.), schemes are often adapted to fit the desired use-case better. 

\section{Practical Application of ABE}
ABE reached the point where it can be applied in pratice and thuse application fields are searched. Since ABE by nature needs an attribute and user managed infrastructe the medical sector fits well. Users as the data owner of their medical record can define access policies so that only authorized doctors can access their medical history. Evaluations about the applicability to mobile devices were conduced by \textit{Akinyele et. al.}, 2011 \cite{akinyele2011securing}. Related to that topic are researches that especially focus on scalability and security by \textit{Li et. al.}, 2013 \cite{li2013scalable} and even later a practical application, evaluation and user case study by \textit{Thatmann et. al.}, 2016 \cite{thatmann2016please} where they analyzed the application of ABE to a hoptial environment. The difference betwen the medical sectors where doctors are the untrusted party, in cloud storage systems the system administrator is the untrusted party. A single authority, as it is usally applied in the medical sector, would indicate an entity with global decryption power thus rendering the direct translation to secure cloud storage system unapplicable.   

Cloud Storage Systems deal with an overhead of authentication and authorization when a cloud storage provider offers a file for download. ABE can eliminate this obstacle by assigning an access policy directly to the cipher text binding the authorization mechansim to the decrytion process it self. \textit{Wang et. al.}, 2010 \cite{Wang:2010:HAE:1866307.1866414} and 2011 \cite{wang2011hierarchical} evaluated a new multi-authority scheme that is based on a hirachical structure on the applicability to cloud storage services. Since the root entity (that one who bootstraps the system) has have global decryption power and so break the end-to-end encryption different other approaches emerged that tried to deescalate the decryption power of the root entity. 

"DAC-MACS: Effective data access control for multiauthority cloud storage systems" 2013 \cite{yang2013dac} created a whole new field of MA-ABE related schemes that tried to improved appon each other (NE-DAC-MACS 2017 \cite{wu2017security}, MAACS 2016 \cite{li2016secure} and TF-DAC-MACS 2017 \cite{li2017two} just to mention few). This schemes focus especially on cloud storage systems and the efficient revocation, encryption and decryption process without having an entity with global decryption power. While this schemes can be already directly applied to real world systems, they do not perfectly fit the requirements stated in section \ref{sec:requirements}. In Chaptur \ref{sec:implementation} TF-DAC-MACS will be used as a baseline to make the needed adaptation to fit it to the stated requirementes. 

\section{Overviews and Comparisons of ABE Schemes}
Since the field of ABE growed to rapidly researches stated to clused the different sub topics of ABE. \textit{Dubey et. al} 2015 \cite{dubeysurvey} conducted a survery about for that time known ABE schemes. She listed adventages and disadventages of those schemes. 

Other overview paper try to evaluate the current field to a specific topic. Since the field of multi-authority ABE with the application to cloud storage systems grow with the DAC-MACS family different survery papers listed techniques, differences, adventages and disadventages \cite{nagarajan2018overview}. 

Mostly this work builds up and extends in Chaptur \ref{sec:concept} the work of \textit{Lee, Chung and Hwang} 2013 \cite{lee2013survey}. They clustered the research field of ABE into different sub-topics, extracted requirementes for the application of cloud environments and finally analyzed the different topics depending on the requirements. However, since their work is condicuted on a theoretical and cytrographical level, a pratical scalability and performance analysis is still missing. This thesis  extends their requirementes and further analysis, by chosing a respective comparable candicate from the different sub-topic of ABE, the performance and scalbility of those schemes. 

% \subsection{Attribute-Based Encryption}
% Attribute Based Encryption (\ac{ABE}), first introduced by Sahai and Waters \cite{sahai2005fuzzy}, is a cryptographic encryption scheme which uses attributes of a user as keys for encryption. This enables the data owner to craft a ciphertext over chosen attributes that can only be decrypted by any entity that holds a super set of matching attributes. Further, it is possible to embed a complex access structure (e.g. access trees) inside the cipher text, where each node contains \textit{\ac{AND}} or \textit{\ac{OR}} threshold gates. This approach is known as Ciphertext-Policy Attribute-Based Encryption (\ac{CP-ABE}) \cite{bethencourt2007ciphertext}. 
% It is also possible to do it the other way around: Associate the user's key with an access policy, formally known as Key-Policy Attribute Based Encryption (\ac{KP-ABE}) 	te{goyal2006attribute}. 
% %Now the encryptor needs only to encrypt a given plain text with the public key of specific attributes so that only users who hold the right keys are able to decrypt the cipher text.

% Both approaches are limited to one attribute authority (\ac{AA}). So only one trusted entity is in charge of issuing attributes and their matching key pairs. However, in the real world we would like to distribute the issuing of attributes over different authorities. A new scheme is needed where different attribute authorities cooperate and communicate across different domains.  

% % The basic idea is, as proposed in \cite{chase2007multi}, to construct for each users a polynomial of degree $d-1$, where $d$ donates the number of attributes in our system. 

% Multi-Authority Attribute Based Encryption (\ac{MA-ABE}), first proposed by Chase 2007 \cite{chase2007multi}, allows multiple attribute authorities to maintain different attribute domains. To ensure collusion resistance between users, a trusted  Central Authority (\ac{CA}) was introduced to assign each user an unique identifier (\ac{UID}) and making the decryption process depending on this \ac{UID}. Its disadvantage is the \ac{CA}'s global decryption power and therefore the necessity to remain trusted. 
% %To prevent collusion between user in a multi authority setting, the challenge for each user needs to be individual. But it still needs to be ensured that the encryption of a message is independent of any user specific identifier, since the encryption progress should sourly depend on the attribute set known to the system.
% %To mitigate this problem a global identifier (\ac{GID} or \ac{UID}) per users was introduced that is shown to each attribute authority (\ac{AA}) to receive the corresponding private key for the users attributes. 
% %The central authority (\ac{CA}) now has to make sure that the user dependent challenge results in a global decryption key to decrypt the message.
% %In fact the \ac{CA} has to be trusted since it computes the users private keys in such a way that on decryption it reveals the global decryption key. 
% Chase \textit{et al.} addressed this issue in \cite{chase2009improving} by distributing the global secret  master key generation over the \ac{AA}s. However, since the global master secret is computed on system initialization, no further \ac{AA}s can be added afterwards without rebooting the system. Also the scheme did not support attribute revocation which rendered it practical not applicable.
% % Each authority uses this seed in combination with a pseudo random function to deterministically create the users private key. Since the \ac{CA} possesses the same seed, same pseudo random function and issues the users \ac{GID}, it can also compute the same private key as issued by the corresponding \ac{AA}. So it can ensure that on decryption the keys add up to reveal the global decryption key. This scheme has a major issue: The \ac{CA} has global decryption power. 

% % Chase notices this problem as well and tried to mitigate it by decentrializing the seed generation \cite{chase2009improving}.  First user attributes could not easly be revoked\footnote{Chase proposed to assign each user a range of \ac{GID}s, so that a user can migrate to the next \ac{GID} on revocation. Since the \ac{GID} range is finite, this solution does not scale.}. Second \ac{AA}'s cant be added on runtime without reissuing each user his keys. And last, the attribute universe is finite (no large-universe). Further we noticed that if a failure of one \ac{AA} renders the system unresponsible, since a cyphertext includes attributes from each authority. 

% Data Access Control for Multi-Authority Cloud Storage Systems (\ac{DAC-MACS}) \cite{yang2013dac} is a scheme that tackles both of this issues. Each authority receives its own ciphertext that depends solely on the attributes issued in this domain. While Chase managed to maintain the "one-plaintext-one-ciphertext" ratio, \ac{DAC-MACS} needs to create $k$ ciphertexts: One per \ac{AA}.\footnote{If the ciphertext does not require any attributes of an specific authority it does not have to create a ciphertext for this domain.} It does not require any coordination between authorities which enables to add new \ac{AA}s at runtime without recreating the user keys. This scheme also includes features for efficient revocation while it claims to maintain forward and backward secrecy. 

% \ac{DAC-MACS} is not collusion resistance on attribute revocation under the active attack model. The scheme \ac{NEDAC-MACS} (New Extended \ac{DAC-MACS}) shows and solves this vulnerability \cite{wu2017security}. Recent studies introduce a more efficient, scalable and secure approaches such as \ac{MAACS} \cite{li2016secure} and \ac{TF-DAC-MACS} (Two-Factor \ac{DAC-MACS} 	te{li2017two}. The \ac{DAC-MACS} family is further known for the proxy decryption technique, first introduced by \cite{li2013matrix}, where a honest-but-curious server helps the user on decryption.

% Priscilla and Nagarajan 2018 \cite{nagarajan2018overview} conducted an analysis of the \ac{DAC-MACS} family. In addition to that work, this thesis will focus on alternative approaches to improve scalability of secure cloud storage systems and analyze the field of \ac{ABE} and \ac{MA-ABE} more deeply.